---
title: "The Highcharter package"
subtitle: "Anh Mai"
format:
  revealjs: 
    slide-number: true
    chalkboard: 
      buttons: false
    preview-links: auto
    logo: images/quarto.png
    css: styles.css
    footer: <https://quarto.org>
    incremental: true  
    theme : simple
resources:
  - demo.pdf
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
#install.packages("highcharter")
library(highcharter)
data(penguins, package = "palmerpenguins") 
```

---

## The Highcharter package

::: {.incremental}
- Make plots (scatterplots, heatmaps, tree maps, etc.)
- Interactive component (zooming, hovering for more info, and more)
- Plots are configured simply
- Customize theme, titles, legends, tooltips, etc.
:::

---

## The hcaes Function

::: {.incremental}

```{.r}
hcaes(x, y, ...)
```

-  "Similar in spirit to ggplot2::aes"
-   used for mapping variables 
-   can also use color and group here as well

:::

---

## The hchart Function

::: {.incremental}

```{.r}
hchart(df,
       "series",
        hcaes(x, y),
        name = "name")
```

-   assigning the 'series' of plot and the variables to use
-   different series: venn, polygon, pie, line, histogram, heatmap, errorbar, boxplot, bar, area
-   use name to customize labels on individual data points
:::

---

## Building different plot elements

::: {.incremental}

```{.r code-line-numbers="|4|5|6|8|9|10|11|12|13"}
hchart(
  df,
  "series",
  hcaes(x, y, group),
  color = color,
  name = "name",
) |>
  hc_title(text = "title") |>
  hc_subtitle(text = "text") |>
  hc_xAxis(title = list(text = "text")) |>
  hc_yAxis(title = list(text = "text")) |>
  hc_add_theme(theme_name) |>
  hc_tooltip(formatter = JS("function(){return this.variable + ' Custom Label';}"))
```

-   very buildable
-   uses pipes, lists, some customizable formatting for tool tips
:::

---

## Example Code

```{.r code-line-numbers="|1|2|3|4"}
hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species)
)
```

---

## Example Plot

```{r}
highcharter::hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species)
)
```


---

## Example Code (customize color and add names to data)

```{.r code-line-numbers="|5|6"}
hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species),
  color = (c("blue","red","green")),
  name = "Penguin measurements"
)
```

---

## Execute Code

```{.r}
hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species),
  color = (c("blue","red","green")),
  name = "Penguin measurements"
)
```

```{r}
hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species),
  color = (c("blue","red","green")),
  name = "Penguin measurements"
)
```

## Labeling our plot with more detail

```{.r code-line-numbers="|7|8|9|10|11|12"}
hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species),
  color = (c("blue","red","green")),
) |>
  hc_title(text = "Strong Positive Relationship between Flipper and Bill Length") |>
  hc_subtitle(text = "Source: Palmer Penguins") |>
  hc_xAxis(title = list(text = "Flipper Length (mm)")) |>
  hc_yAxis(title = list(text = "Beak Length (mm)")) |>
  hc_add_theme(hc_theme_smpl()) |>
  hc_tooltip(formatter = JS("function(){return this.point.island + ' Island';}"))

```

---

## The plot!

```{r}
hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species),
  color = (c("blue","red","green"))
) |>
  hc_title(text = "Strong Positive Relationship between Flipper and Bill Length in Penguins near Palmer Station, Antarctica") |>
  hc_subtitle(text = "Source: Palmer Penguins") |>
  hc_xAxis(title = list(text = "Flipper Length (mm)")) |>
  hc_yAxis(title = list(text = "Beak Length (mm)")) |>
  hc_add_theme(hc_theme_smpl()) |>
  hc_tooltip(formatter = JS("function(){return this.point.island + ' Island';}"))
```

---

## Thanks!

Any questions?
Here's the code we covered today!

::: aside 
Sources:
https://www.datanovia.com/en/lessons/highchart-interactive-scatter-plot-in-r/#google_vignette, https://jkunst.com/highcharter/reference/index.html

:::
<style>
  .column {
    line-height: 1.2;
  }
</style>

:::: {.columns}

::: {.column width="40%"}
hcaes()  
hchart()  
hc_title()  
hc_subtitle()  
hc_xAxis()  
hc_yAxis()  
hc_add_theme()  
hc_tooltip()  
:::

::: {.column width="60%"}
Mapping function  
Function to create plot  
Labeling  
:::

::::